Examination of shapes! (homework exam)

### 2016-02-19 geometricAlgorithms/homeworkExam/homeworkExam.tex
yesterdays modifications

% "define" Scala
\lstdefinelanguage{scala}{
  morekeywords={abstract,case,catch,class,def,%
    do,else,extends,false,final,finally,%
    for,if,implicit,import,match,mixin,%
    new,null,object,override,package,%
    private,protected,requires,return,sealed,%
    super,this,throw,trait,true,try,%
    type,val,var,while,with,yield},
  otherkeywords={=>,<-,<\%,<:,>:,\#,@},
  sensitive=true,
  morecomment=[l]{//},
  morecomment=[n]{/*}{*/},
  morestring=[b]",
  morestring=[b]',
  morestring=[b]"""
}
\begin{document}
\begin{empfile}
\begin{empcmds}
input metauml;
\end{empcmds}
\author{Jappie Klooster}
\title{Stay in Shape! A geometric algorithmic excersize collection}
\maketitle

\section{Introduction}
Referencing he book Computational geometry algorithms and application.
This collection  tries to solve a selection of the excersizes in that book.

Referer to this work with care as its meant to be homework (although
I try to make it correct).

\section{The intersection detection problem}
The intersection detection problem for a set S of n line segments is to
determine whether there exists a pair of segments in S that intersect. Give
a plane sweep algorithm that solves the intersection detection problem in
$O(n \cdot  log_2(n))$ time.

\begin{algorithmic}
	\State Sort all line segment $s \in S$ end points $p$ based on
		$y$ coordinate.
		$p$ should have a reference to its coorisponding point (ie the start
		point has a reference to the end point and vice versa). The resulting
		collection is called $E_{sorted}$
	\For{point$\in E_{sorted}$}
		\State
		\If{begin point} insert in State. On inserted point calculate
		if there is a crossing if so insert in $E_{sorted}$.
		\EndIf
		\If{end point} remove begin point from state.
		\EndIf
		\If{Crossing point} add to result.
		\EndIf
	\EndFor
\end{algorithmic}

\end{empfile}
\end{document}

>>>>

% "define" Scala
\lstdefinelanguage{scala}{
  morekeywords={abstract,case,catch,class,def,%
    do,else,extends,false,final,finally,%
    for,if,implicit,import,match,mixin,%
    new,null,object,override,package,%
    private,protected,requires,return,sealed,%
    super,this,throw,trait,true,try,%
    type,val,var,while,with,yield},
  otherkeywords={=>,<-,<\%,<:,>:,\#,@},
  sensitive=true,
  morecomment=[l]{//},
  morecomment=[n]{/*}{*/},
  morestring=[b]",
  morestring=[b]',
  morestring=[b]"""
}
\begin{document}
\begin{empfile}
\begin{empcmds}
input metauml;
\end{empcmds}
\author{Jappie Klooster}
\title{Examination of shapes! (homework exam)}
\maketitle

\section{Polyhedron}

\subsection{When is the $xy$-silhouette of a convex polyhedron $P$ is unique}
%TODO this anwser seems to complex for 0.5 points, maybe I should look in the book
% TODO: don't give a crappy discription
%TODO: define uniqueness?
First we have to define what uniqueness means to anwser this question. I'm 
assuming uniqueness in this case means an $xy$-silhouette that can only be
generated from a polyhedron P when looking at it from a specific angle.

% TODO: wtf?
So there existions a quaternion $\exists q \in Q$ where there is an $xy$-silhoeutte
$s$ that is not equal to any other sillhoute.

So an $xy$ sillhouette is unique if there is no repitition in the outer plan that
can be reshown trough rotation.

Although it does have to be notated that you can always flip the entire thing 180
degree and receive the exact sam sillhoutte.

\subsubsection{When it is not unique}
%TODO: \dots
\subsection{Give an algorithm that detrmines an $xy$-silhouette of a conves polyhedron $P$ in O(n) time}
\begin{algorithmic}
	\State Sort all line segment $s \in S$ end points $p$ based on
		$y$ coordinate.
		$p$ should have a reference to its coorisponding point (ie the start
		point has a reference to the end point and vice versa). The resulting
		collection is called $E_{sorted}$
	\For{point$\in E_{sorted}$}
		\State
		\If{begin point} insert in State. On inserted point calculate
		if there is a crossing if so insert in $E_{sorted}$.
		\EndIf
		\If{end point} remove begin point from state.
		\EndIf
		\If{Crossing point} add to result.
		\EndIf
	\EndFor
\end{algorithmic}

\subsection{Why takes this algorithm linear time}
\section{Red and blue lines}
\section{Polygon cut}
\section{Diagonal polygon cut}
\end{empfile}
\end{document}
